\documentclass[12pt,a4paper]{report}

% ------------------------------------------------
% PACKAGES
% ------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[table]{xcolor}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[most]{tcolorbox}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{pifont}

\usetikzlibrary{arrows.meta, positioning, shapes.geometric, shapes.misc}
\pgfplotsset{compat=1.18}

% ------------------------------------------------
% PAGE SETUP
% ------------------------------------------------
\geometry{margin=1in}
\onehalfspacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% ------------------------------------------------
% COLOR THEME
% ------------------------------------------------
\definecolor{primary}{HTML}{4B2E83}
\definecolor{secondary}{HTML}{EDE7F6}
\definecolor{accent}{HTML}{00897B}
\definecolor{softteal}{HTML}{E0F2F1}
\definecolor{softcream}{HTML}{FFF8E1}
\definecolor{softrose}{HTML}{FCE4EC}
\definecolor{softgray}{HTML}{F5F5F5}
\definecolor{darkgray}{HTML}{333333}

% ------------------------------------------------
% HYPERLINK SETUP
% Contents, List of Figures, and List of Tables are black
% ------------------------------------------------
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black
}

% ------------------------------------------------
% HEADER AND FOOTER
% ------------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Information System Analysis Report}
\fancyhead[R]{NextStepBD}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ------------------------------------------------
% TITLE FORMATTING
% ------------------------------------------------
\titleformat{\chapter}
  {\normalfont\huge\bfseries\color{primary}}
  {Chapter \thechapter}
  {20pt}
  {}

\titleformat{\section}
  {\normalfont\Large\bfseries\color{primary}}
  {\thesection}
  {1em}
  {}

\titleformat{\subsection}
  {\normalfont\large\bfseries\color{accent}}
  {\thesubsection}
  {1em}
  {}

\titleformat{\subsubsection}
  {\normalfont\normalsize\bfseries\color{primary}}
  {}
  {0pt}
  {}

% ------------------------------------------------
% CUSTOM BOXES
% ------------------------------------------------
\newtcolorbox{highlightBox}{
    enhanced,
    colback=secondary,
    colframe=primary,
    boxrule=1pt,
    arc=1mm,
    left=9pt,
    right=9pt,
    top=9pt,
    bottom=9pt,
    borderline west={4pt}{0pt}{primary}
}

\newtcolorbox{problemBox}{
    enhanced,
    colback=softrose,
    colframe=primary!80!black,
    boxrule=1pt,
    arc=1mm,
    left=9pt,
    right=9pt,
    top=9pt,
    bottom=9pt,
    fonttitle=\bfseries,
    title=\textbf{Problem Statement},
    borderline west={4pt}{0pt}{primary!80!black}
}

\newtcolorbox{summaryBox}{
    enhanced,
    colback=softteal,
    colframe=accent,
    boxrule=1pt,
    arc=1mm,
    left=9pt,
    right=9pt,
    top=9pt,
    bottom=9pt,
    fonttitle=\bfseries,
    title=\textbf{Feasibility Summary},
    borderline west={4pt}{0pt}{accent}
}

\newtcolorbox{recommendBox}{
    enhanced,
    colback=softcream,
    colframe=orange!80!black,
    boxrule=1.3pt,
    arc=1mm,
    left=11pt,
    right=11pt,
    top=12pt,
    bottom=10pt,
    fonttitle=\bfseries\large,
    title=\textbf{\ding{72} Recommended Action},
    attach boxed title to top left={xshift=5mm,yshift=-2mm},
    boxed title style={
        colback=orange!80!black,
        colframe=orange!80!black,
        coltext=white,
        arc=1mm
    },
    borderline west={5pt}{0pt}{orange!80!black}
}

\newtcolorbox{noteBox}{
    enhanced,
    colback=softgray,
    colframe=primary,
    boxrule=1pt,
    arc=1mm,
    left=9pt,
    right=9pt,
    top=9pt,
    bottom=9pt,
    borderline west={4pt}{0pt}{primary}
}

% ------------------------------------------------
% DOCUMENT START
% ------------------------------------------------
\begin{document}

% ------------------------------------------------
% TITLE PAGE
% ------------------------------------------------
\begin{titlepage}
    \centering
    \vspace*{1cm}

    {\Large \textbf{Information System Analysis and Design}}\\[0.4cm]
    {\large Academic Laboratory Report}\\[1.4cm]

    {\Huge \textbf{NextStepBD}}\\[0.4cm]
    {\Large Information System Analysis Report}\\[1.2cm]

    \begin{tcolorbox}[
        colback=secondary,
        colframe=primary,
        width=0.9\textwidth,
        arc=4mm,
        boxrule=1pt
    ]
        \centering
        {\Large \textbf{Chapter 1: Recognition of Need}}\\[0.2cm]
        {\Large \textbf{Chapter 2: Initial Feasibility Study}}
    \end{tcolorbox}

    \vspace{1.4cm}

    \textbf{Prepared For:}\\
    Course Teacher Name\\
    Department Name\\
    University Name\\[1.2cm]

    \textbf{Prepared By:}\\
    Team NextStepBD\\
    Group Members Name\\[1.2cm]

    \textbf{Subject Company:}\\
    NextStepBD\\[1cm]

    \vfill
    {\large \today}
\end{titlepage}

\tableofcontents
\listoffigures
\listoftables
\newpage

% ================================================================
% CHAPTER 1
% ================================================================
\chapter{Recognition of Need}

\section{Introduction}

NextStepBD is a Bangladesh-based technology company that provides software development, automation solutions, and consultancy services. The company focuses on building customized digital solutions for local and international clients. Its work environment is fast-moving and client-driven, where quick communication, flexible decision-making, and rapid project execution are important for daily operations.

The company provides both product-based and service-based solutions. Its product development activities include standalone software systems such as doctor management systems, AI-based customer support platforms, and sales automation tools. Alongside software development, NextStepBD also provides consultancy services for internal workflow automation. One notable example is an automation solution where sales data collected through SMS was entered into a centralized software system for analytics, inventory tracking, and supply chain reporting.

\begin{highlightBox}
\textbf{Recognition of Need:} NextStepBD has a functional working system, but the system is not fully centralized. The company uses several separate tools for communication, development, reporting, and coordination. This creates a need for a more integrated information system that can support future growth.
\end{highlightBox}

The company currently relies on a combination of custom-built tools and commonly used platforms such as Microsoft Excel, Google Sheets, GitHub, WhatsApp, Slack, and Email. These tools are useful individually, but they are not connected through a single system. As a result, managers and employees often need to coordinate manually, transfer information between platforms, and search through different communication channels to find project-related information.

\section{Company Overview}

NextStepBD operates as an IT-based software and automation company. Its business model is based on delivering customized digital solutions according to client needs. The company works with software systems, AI-based tools, workflow automation, and customer support solutions. This makes the organization dependent on accurate requirement collection, strong coordination between teams, proper task assignment, and reliable communication with clients.

The organizational structure of NextStepBD is relatively flat. This helps the company make decisions quickly and respond to client requests faster. However, the same structure also creates dependency on a limited number of managers or coordinators. These individuals often act as the bridge between clients and developers. If proper documentation and task tracking systems are not maintained, the workflow can become unclear and difficult to scale.

\begin{table}[H]
\centering
\caption{NextStepBD -- Organizational Profile}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{4cm}|X|}
\hline
\rowcolor{secondary}
\textbf{Area} & \textbf{Description} \\
\hline
Company Name & NextStepBD \\
\hline
Business Type & IT-based software development, automation, and consultancy company \\
\hline
Core Activities & Customized software development, workflow automation, AI-based support tools, sales automation, and reporting solutions \\
\hline
Working Style & Client-driven, flexible, fast communication-based, and semi-structured \\
\hline
Current Operational Approach & Uses multiple separate tools for communication, development, reporting, and coordination \\
\hline
Major Need & A centralized and integrated information system to improve coordination, tracking, reporting, and scalability \\
\hline
\end{tabularx}
\end{table}

\section{Business Activities and Service Context}

NextStepBD serves clients by designing and developing software systems that solve practical business problems. The company’s services can be understood through three major areas: software development, automation consultancy, and customer support solutions.

In software development, the company builds standalone systems based on client requirements. These systems may include management software, operational software, or business-specific applications. In automation consultancy, NextStepBD helps organizations reduce manual work by designing automated workflows. For example, sales data collection through SMS and automatic entry into a reporting system shows how the company uses technology to improve business efficiency. In customer support solutions, the company helps businesses manage social media communication and client interactions more effectively.

These activities require continuous communication between clients, managers, and developers. Requirements must be collected clearly, tasks must be assigned properly, progress must be tracked, and reports must be prepared accurately. Therefore, the quality of the company’s internal information system directly affects project delivery and client satisfaction.

\section{Existing System and Tools Used}

The current system of NextStepBD is not based on one centralized platform. Instead, it is formed by a combination of several digital tools. WhatsApp is heavily used for fast communication with clients and internal teams. Slack is used mainly for more structured or international collaboration. Email is used for formal communication and final reporting. GitHub supports development and version control. Excel and Google Sheets are used for reporting, data management, financial records, and client-side collaboration.

This tool-based system gives flexibility, but it also creates fragmentation. Information about the same project may exist in WhatsApp messages, Google Sheets, GitHub repositories, and email threads. A manager may need to check multiple platforms to understand the actual progress of a project. Similarly, developers may receive instructions from chat messages while technical updates are maintained in GitHub. This separation creates a gap between communication and execution.

\begin{table}[H]
\centering
\caption{Current Tools and Their Operational Role}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{4cm}|X|}
\hline
\rowcolor{secondary}
\textbf{Tool / Platform} & \textbf{Operational Role} \\
\hline
WhatsApp & Used for quick client communication, internal coordination, informal discussions, and urgent updates. \\
\hline
Slack & Used for structured team communication and international collaboration in selected cases. \\
\hline
Email & Used for formal communication, official document sharing, and final report delivery. \\
\hline
GitHub & Used for source code management, version control, and developer collaboration. \\
\hline
Microsoft Excel and Google Sheets & Used for reporting, financial records, shared data handling, and client-side collaboration. \\
\hline
Custom Tools & Used for automation, data processing, analytics, and workflow support in specific projects. \\
\hline
\end{tabularx}
\end{table}

\begin{figure}[H]
\centering
\resizebox{0.95\textwidth}{!}{
\begin{tikzpicture}[
    every node/.style={font=\scriptsize},
    tool/.style={
        rectangle,
        rounded corners,
        draw=accent,
        fill=softteal,
        thick,
        text width=2.4cm,
        minimum height=0.9cm,
        align=center
    },
    center/.style={
        circle,
        draw=primary,
        fill=secondary,
        thick,
        text width=2.3cm,
        minimum size=2.4cm,
        align=center
    },
    arrow/.style={thick, -{Latex[length=2.5mm]}, color=primary}
]

\node[center] (ops) at (0,0) {Current\\Operations};

\node[tool] (wa) at (-5,2) {WhatsApp};
\node[tool] (slack) at (0,3) {Slack};
\node[tool] (email) at (5,2) {Email};
\node[tool] (github) at (-5,-2) {GitHub};
\node[tool] (excel) at (0,-3) {Excel};
\node[tool] (sheets) at (5,-2) {Google Sheets};

\draw[arrow] (wa) -- (ops);
\draw[arrow] (slack) -- (ops);
\draw[arrow] (email) -- (ops);
\draw[arrow] (github) -- (ops);
\draw[arrow] (excel) -- (ops);
\draw[arrow] (sheets) -- (ops);

\end{tikzpicture}
}
\caption{Current Tool-Based Operational Environment}
\end{figure}

\section{Current Workflow}

The current workflow of NextStepBD begins when a client communicates requirements through WhatsApp, shared documents, Google Sheets, or email. The manager reviews the requirement and assigns tasks to developers. Developers then work on the assigned task using GitHub for version control. During development, internal communication takes place mainly through WhatsApp groups or direct messages. After the work is completed, reports are prepared using Excel or Google Sheets and delivered to the client through email or shared links.

This workflow is practical for a small team and allows quick communication. However, it becomes less effective as the number of projects, clients, and developers increases. Since the workflow depends on manual coordination, project information can become scattered. For example, the client’s requirement may be in WhatsApp, task progress may be in GitHub, and final reporting may be in Google Sheets. Without a centralized system, it becomes difficult to maintain a single source of truth.

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tikzpicture}[
    node distance=1cm,
    every node/.style={font=\scriptsize},
    step/.style={
        rectangle,
        rounded corners,
        draw=primary,
        fill=secondary,
        thick,
        text width=2.5cm,
        minimum height=0.9cm,
        align=center
    },
    risk/.style={
        rectangle,
        rounded corners,
        draw=orange!80!black,
        fill=softcream,
        thick,
        text width=2.5cm,
        minimum height=0.9cm,
        align=center
    },
    arrow/.style={thick, -{Latex[length=2.5mm]}, color=primary}
]

\node[step] (client) {Client\\Requirement};
\node[step, right=of client] (manager) {Manager\\Review};
\node[step, right=of manager] (assign) {Task\\Assignment};
\node[step, right=of assign] (dev) {Developer\\Work};
\node[step, below=of dev] (github) {GitHub\\Version Control};
\node[risk, left=of github] (chat) {WhatsApp\\Coordination};
\node[step, left=of chat] (report) {Excel / Sheets\\Reporting};
\node[step, left=of report] (delivery) {Email / Shared\\Delivery};

\draw[arrow] (client) -- (manager);
\draw[arrow] (manager) -- (assign);
\draw[arrow] (assign) -- (dev);
\draw[arrow] (dev) -- (github);
\draw[arrow] (github) -- (chat);
\draw[arrow] (chat) -- (report);
\draw[arrow] (report) -- (delivery);

\end{tikzpicture}
}
\caption{Current Operational Workflow of NextStepBD}
\end{figure}

\begin{highlightBox}
\textbf{System Observation:} The existing workflow works, but it is heavily dependent on manual communication. The system lacks a centralized dashboard where requirements, tasks, development progress, reports, and decisions can be tracked together.
\end{highlightBox}

\section{Need for System Improvement}

The main need for improvement comes from the gap between the company’s growing operational requirements and its current semi-structured information system. As NextStepBD handles more clients and more development tasks, the existing tool-based workflow may become difficult to manage. Manual coordination can slow down decision-making, increase dependency on managers, and create confusion among developers.

A modern information system should not only store data but also connect people, processes, and tools. For NextStepBD, this means the improved system should connect client requirements, task assignment, developer work, communication history, reporting data, and project status. Such a system would help managers monitor progress, developers understand priorities, and clients receive more structured updates.

The need is therefore not simply to introduce new software. The actual need is to create a more organized and integrated work environment where every project has clear requirements, assigned tasks, documented communication, visible progress, and reliable reporting.

\section{Problem Identification}

Through observation of the company’s operations, informal interviews with team members, and analysis of the current workflow, six major problem areas have been identified. These problems are common in growing technology companies that depend on multiple disconnected tools.

\subsection{Problem 01: Fragmented System and Lack of Integration}

\begin{problemBox}
NextStepBD currently operates using multiple disconnected tools such as WhatsApp, Google Sheets, Excel, GitHub, Slack, and Email. While each tool serves a specific purpose, there is no centralized system that integrates all operations into a unified platform.
\end{problemBox}

The main issue is not the use of these tools individually, but the absence of connection between them. Communication, development, reporting, and task tracking remain separated. This leads to data duplication, inconsistency, and difficulty in maintaining a single source of truth. Employees may need to manually transfer information from one platform to another, which increases the chance of error and reduces efficiency.

\subsection{Problem 02: Over-Reliance on Informal Communication Channels}

\begin{problemBox}
WhatsApp plays a dominant role in both internal and external communication. Although it enables fast communication, it is not designed as a professional project management, documentation, or decision-tracking platform.
\end{problemBox}

Important discussions, client requirements, approvals, and decisions can become buried inside long chat threads. This makes it difficult to retrieve previous decisions or verify who approved a particular change. Since WhatsApp does not provide structured task tracking, responsibilities and deadlines may remain unclear.

\subsection{Problem 03: Unstructured Workflow and Weak Requirement Management}

\begin{problemBox}
The current workflow lacks a formal requirement collection and approval process. Client requirements are often communicated through messages or shared documents without following a standard format.
\end{problemBox}

When requirements are incomplete or unclear, developers may need to make assumptions. This can create a mismatch between client expectations and delivered output. Frequent changes without proper documentation can also increase rework and delay project delivery.

\subsection{Problem 04: Absence of Centralized Task and Project Management System}

\begin{problemBox}
Task assignment and project tracking are mostly handled through manual communication. There is no dedicated centralized system to manage tasks, deadlines, dependencies, ownership, and progress tracking.
\end{problemBox}

Managers often need to follow up manually with developers to know task status. Developers may also face confusion about priority and deadlines. Without a centralized dashboard, it becomes difficult to identify bottlenecks, delayed tasks, or overloaded team members.

\subsection{Problem 05: Inefficient Data Management and Reporting}

\begin{problemBox}
The company relies heavily on Microsoft Excel and Google Sheets for reporting and data management. These tools are useful for basic tasks but become inefficient when data volume increases or multiple users update files manually.
\end{problemBox}

Data may become scattered across different files and versions. Manual reporting increases the possibility of calculation errors, outdated information, and inconsistent records. The absence of real-time dashboards also limits management’s ability to make fast and informed decisions.

\subsection{Problem 06: Scalability and Dependency Issues}

\begin{problemBox}
As the company grows, the current workflow creates dependency on specific individuals, especially managers who coordinate between clients and developers.
\end{problemBox}

If key persons are unavailable, task assignment, requirement clarification, reporting, and decision-making may be delayed. The lack of documented processes also makes it difficult to onboard new employees quickly. This creates scalability challenges for future growth.

\section{Problem Severity Overview}

The following graph shows the estimated severity level of the identified problems based on their impact on productivity, communication, accountability, and scalability.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    xbar,
    width=0.95\textwidth,
    height=7cm,
    xmin=0,
    xmax=10,
    xlabel={Severity Score},
    symbolic y coords={
        Scalability,
        Reporting,
        Task Management,
        Requirement,
        Communication,
        Integration
    },
    ytick=data,
    nodes near coords,
    grid=major,
    major grid style={draw=gray!25},
    title={Problem Severity Assessment}
]
\addplot[fill=primary!75] coordinates {
    (7,Scalability)
    (8,Reporting)
    (9,{Task Management})
    (9,Requirement)
    (8,Communication)
    (10,Integration)
};
\end{axis}
\end{tikzpicture}
\caption{Estimated Severity of Identified Problems}
\end{figure}

\section{Chapter 1 Conclusion}

The recognition of need shows that NextStepBD has successfully established a functional working system using available digital tools. However, the system lacks the structure, integration, and centralized control required for sustainable growth.

The major challenges include fragmented systems, over-reliance on informal communication, unstructured requirement management, absence of centralized task tracking, inefficient reporting, and scalability limitations. These problems are connected to each other. For example, weak requirement management creates task confusion, task confusion increases communication dependency, and scattered communication makes reporting less reliable.

Therefore, the company needs an integrated information system that can connect communication, requirement management, task tracking, development workflow, reporting, and documentation. Chapter 2 analyzes the feasibility of solving these problems using technical, economic, and operational perspectives.

\newpage

% ================================================================
% CHAPTER 2
% ================================================================
\chapter{Initial Feasibility Study}

\section{Introduction}

This chapter presents an initial feasibility study for the six major problems identified in Chapter 1. The purpose of this chapter is to evaluate whether the proposed improvements are technically possible, economically reasonable, and operationally acceptable for NextStepBD.

The feasibility framework used in this chapter follows the standard \textbf{Technical, Economic, and Operational} model.

\begin{noteBox}
\textbf{Feasibility Focus:} The objective of this chapter is not only to propose solutions, but also to determine which solutions are realistic, affordable, and suitable for NextStepBD's current operational environment.
\end{noteBox}

\begin{table}[H]
\centering
\caption{TEO Feasibility Evaluation Criteria}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{4cm}|X|}
\hline
\rowcolor{secondary}
\textbf{Feasibility Dimension} & \textbf{Evaluation Question} \\
\hline
\textbf{Technical Feasibility} & Can the proposed solution be implemented using available technology, tools, infrastructure, and technical skills? \\
\hline
\textbf{Economic Feasibility} & Are the expected benefits greater than the cost of implementation, training, operation, and maintenance? \\
\hline
\textbf{Operational Feasibility} & Can the organization realistically adopt and continue using the solution within its existing workflow and culture? \\
\hline
\end{tabularx}
\end{table}

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tikzpicture}[
    node distance=1.6cm,
    every node/.style={font=\scriptsize},
    process/.style={
        rectangle,
        rounded corners,
        draw=primary,
        fill=secondary,
        thick,
        text width=2.7cm,
        minimum height=0.9cm,
        align=center
    },
    decision/.style={
        diamond,
        draw=accent,
        fill=softcream,
        thick,
        aspect=1.8,
        text width=2.2cm,
        align=center
    },
    arrow/.style={thick, -{Latex[length=2.5mm]}, color=primary}
]

\node[process] (need) {Need\\Recognition};
\node[process, right=of need] (analysis) {TEO\\Analysis};
\node[decision, right=of analysis] (decision) {Decision};
\node[process, below=1.4cm of decision] (pilot) {Pilot\\Implementation};
\node[process, left=of pilot] (monitor) {Monitoring\\and Feedback};
\node[process, left=of monitor] (scale) {Full-Scale\\Adoption};

\draw[arrow] (need) -- (analysis);
\draw[arrow] (analysis) -- (decision);
\draw[arrow] (decision) -- node[right, font=\scriptsize]{Feasible} (pilot);
\draw[arrow] (pilot) -- (monitor);
\draw[arrow] (monitor) -- (scale);
\draw[arrow] (scale) |- (need);
\draw[arrow, dashed] (decision.north) -- ++(0,0.9) -| node[above, font=\scriptsize]{Revise / Defer} (analysis.north);

\end{tikzpicture}
}
\caption{Initial Feasibility Governance Cycle for NextStepBD}
\end{figure}

\section{Initial Feasibility Analysis}

\subsection{Problem 01: Fragmented System and Lack of Integration}

\begin{problemBox}
NextStepBD uses multiple disconnected platforms such as WhatsApp, GitHub, Google Sheets, Excel, Slack, and Email. There is no centralized system that connects communication, requirement collection, development progress, task management, and reporting.
\end{problemBox}

\begin{summaryBox}
An integrated workflow management system is technically feasible because several cloud-based platforms support integration with GitHub, Google Workspace, Slack, and Email. Economically, it can reduce manual work and coordination delays. Operationally, it is suitable if implemented gradually.
\end{summaryBox}

\subsubsection{Details of Findings}

\begin{itemize}[leftmargin=*]
    \item \textbf{Technical Feasibility:} Jira, ClickUp, Notion, Zoho Projects, Monday.com, and GitHub Projects can integrate task management, document storage, reporting, and communication.
    \item \textbf{Economic Feasibility:} Estimated annual cost may range from BDT 3--8 lakhs. The cost is justified by reduced manual coordination, fewer errors, and faster reporting.
    \item \textbf{Operational Feasibility:} Employees already use digital tools, so adoption is realistic with proper training and policies.
    \item \textbf{Risk Assessment:} Resistance from employees can be reduced through pilot implementation and management support.
\end{itemize}

\begin{table}[H]
\centering
\caption{Integrated System Implementation -- TEO Feasibility Summary}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{3cm}|p{2.5cm}|X|}
\hline
\rowcolor{secondary}
\textbf{Dimension} & \textbf{Rating} & \textbf{Justification} \\
\hline
Technical & High & Cloud-based tools can connect GitHub, Google Sheets, Slack, and Email. \\
\hline
Economic & High & Reduces manual work, reporting delay, duplication, and coordination cost. \\
\hline
Operational & Medium & Requires training, policy development, and gradual adoption. \\
\hline
Overall Viability & Feasible & Recommended for early implementation. \\
\hline
\end{tabularx}
\end{table}

\begin{recommendBox}
\textbf{Priority Action:} Adopt a centralized project and workflow management platform within 3--4 months.

\textbf{Business Value:} This will reduce manual coordination, improve task visibility, and create a single reliable source for project information.

\textbf{Implementation Note:} Begin with a small pilot project before full organizational adoption.
\end{recommendBox}

\subsection{Problem 02: Over-Reliance on Informal Communication Channels}

\begin{problemBox}
WhatsApp is heavily used for client communication and internal coordination, but it is not designed for official documentation, task assignment, decision tracking, or project monitoring.
\end{problemBox}

\begin{summaryBox}
A structured communication policy is feasible. WhatsApp can remain available for quick updates, but formal decisions, approvals, task updates, and requirements should be recorded in a centralized system.
\end{summaryBox}

\subsubsection{Details of Findings}

\begin{itemize}[leftmargin=*]
    \item \textbf{Technical Feasibility:} Slack, Microsoft Teams, Google Chat, and project platforms can provide searchable channels and structured records.
    \item \textbf{Economic Feasibility:} Since Slack is already used, better utilization would not require a major extra investment.
    \item \textbf{Operational Feasibility:} Employees are already familiar with chat-based communication, making the transition practical.
    \item \textbf{Risk Assessment:} Employees may continue using WhatsApp informally unless communication rules are clearly defined.
\end{itemize}

\begin{table}[H]
\centering
\caption{Communication System -- Current State vs Proposed State}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{4cm}|X|X|}
\hline
\rowcolor{secondary}
\textbf{Area} & \textbf{Current State} & \textbf{Proposed State} \\
\hline
Client Communication & Mostly WhatsApp and Email & Structured communication log with Email and project portal \\
\hline
Internal Discussion & WhatsApp groups & Slack or project-based official channels \\
\hline
Decision Tracking & Difficult to retrieve & Decisions recorded in centralized system \\
\hline
Task Assignment & Informal messages & Assigned through task board with deadline \\
\hline
Documentation & Scattered & Searchable and centralized \\
\hline
\end{tabularx}
\end{table}

\begin{recommendBox}
\textbf{Priority Action:} Introduce a formal communication policy.

\textbf{Business Value:} This will reduce lost information and improve accountability.

\textbf{Implementation Note:} Urgent messages may remain on WhatsApp, but requirements, approvals, and task updates must be documented officially.
\end{recommendBox}

\subsection{Problem 03: Unstructured Workflow and Weak Requirement Management}

\begin{problemBox}
Client requirements are often received through messages or shared documents without a standard requirement format. This creates incomplete, unclear, or frequently changing requirements.
\end{problemBox}

\begin{summaryBox}
A structured requirement management process is highly feasible. NextStepBD can introduce requirement templates, approval checkpoints, and change request forms with low cost.
\end{summaryBox}

\subsubsection{Details of Findings}

\begin{itemize}[leftmargin=*]
    \item \textbf{Technical Feasibility:} Google Forms, Notion, Jira, ClickUp, GitHub Issues, or a custom portal can manage requirements.
    \item \textbf{Economic Feasibility:} The cost is low because the company already uses digital tools.
    \item \textbf{Operational Feasibility:} Managers, developers, and clients will benefit from clearer requirement documentation.
    \item \textbf{Risk Assessment:} The requirement format must remain simple so that clients and managers actually use it.
\end{itemize}

\begin{table}[H]
\centering
\caption{Proposed Requirement Management Template}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{4cm}|X|}
\hline
\rowcolor{secondary}
\textbf{Field} & \textbf{Purpose} \\
\hline
Requirement ID & Provides a unique identification number for tracking. \\
\hline
Client Name & Identifies the source of the requirement. \\
\hline
Requirement Description & Explains what needs to be developed. \\
\hline
Priority & Defines whether the requirement is High, Medium, or Low priority. \\
\hline
Acceptance Criteria & Defines when the requirement will be considered complete. \\
\hline
Responsible Person & Assigns ownership to a manager or developer. \\
\hline
Approval Status & Shows whether the requirement is Pending, Approved, Revised, or Rejected. \\
\hline
Change History & Records modifications and updates. \\
\hline
\end{tabularx}
\end{table}

\begin{recommendBox}
\textbf{Priority Action:} Create a lightweight Software Requirement Specification template.

\textbf{Business Value:} This will reduce misunderstanding, improve requirement clarity, and decrease rework.

\textbf{Implementation Note:} Start with a short form before introducing a detailed SRS format.
\end{recommendBox}

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tikzpicture}[
    node distance=1.1cm,
    every node/.style={font=\scriptsize},
    step/.style={
        rectangle,
        rounded corners,
        draw=accent,
        fill=softteal,
        thick,
        text width=2.5cm,
        minimum height=0.85cm,
        align=center
    },
    arrow/.style={thick, -{Latex[length=2.5mm]}, color=primary}
]

\node[step] (client) {Client\\Requirement};
\node[step, right=of client] (template) {Requirement\\Template};
\node[step, right=of template] (review) {Manager\\Review};
\node[step, right=of review] (approve) {Client\\Approval};

\node[step, below=1.3cm of approve] (task) {Task\\Creation};
\node[step, left=of task] (dev) {Development\\Work};
\node[step, left=of dev] (test) {Testing and\\Feedback};
\node[step, left=of test] (delivery) {Final\\Delivery};

\draw[arrow] (client) -- (template);
\draw[arrow] (template) -- (review);
\draw[arrow] (review) -- (approve);
\draw[arrow] (approve) -- (task);
\draw[arrow] (task) -- (dev);
\draw[arrow] (dev) -- (test);
\draw[arrow] (test) -- (delivery);
\draw[arrow, dashed] (test.north) |- node[left, font=\scriptsize]{Revision Required} (review.south);

\end{tikzpicture}
}
\caption{Proposed Requirement-to-Delivery Workflow}
\end{figure}

\subsection{Problem 04: Absence of Centralized Task and Project Management System}

\begin{problemBox}
Task assignment and project progress tracking are mainly handled through manual communication. There is no single dashboard for deadlines, dependencies, progress, bottlenecks, and responsibility.
\end{problemBox}

\begin{summaryBox}
A centralized task and project management system is highly feasible. Since the company already uses GitHub, task management can be integrated with GitHub Issues, pull requests, and project boards.
\end{summaryBox}

\subsubsection{Details of Findings}

\begin{itemize}[leftmargin=*]
    \item \textbf{Technical Feasibility:} GitHub Projects, Jira, ClickUp, Trello, and Zoho Projects can provide Kanban boards, deadlines, and task ownership.
    \item \textbf{Economic Feasibility:} GitHub Projects can be used at low cost, while advanced platforms may be adopted later.
    \item \textbf{Operational Feasibility:} Developers already use GitHub, making adoption practical.
    \item \textbf{Risk Assessment:} The dashboard will be unreliable if task status is not updated regularly.
\end{itemize}

\begin{table}[H]
\centering
\caption{Task Management System -- TEO Feasibility Summary}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{3cm}|p{2.5cm}|X|}
\hline
\rowcolor{secondary}
\textbf{Dimension} & \textbf{Rating} & \textbf{Justification} \\
\hline
Technical & High & GitHub Projects and other project tools are suitable for software teams. \\
\hline
Economic & High & Low-cost implementation with strong productivity benefit. \\
\hline
Operational & High & Developers already use GitHub, making adoption practical. \\
\hline
Overall Viability & Highly Feasible & Recommended for immediate implementation. \\
\hline
\end{tabularx}
\end{table}

\begin{recommendBox}
\textbf{Priority Action:} Implement GitHub Projects or a similar centralized task management system.

\textbf{Business Value:} This will improve task visibility, reduce manual follow-up, and help managers identify bottlenecks.

\textbf{Implementation Note:} Every task should include owner, deadline, priority, status, and related GitHub issue.
\end{recommendBox}

\subsection{Problem 05: Inefficient Data Management and Reporting}

\begin{problemBox}
NextStepBD relies heavily on Excel and Google Sheets for reporting and data management. These tools become inefficient when data volume increases or multiple users update files manually.
\end{problemBox}

\begin{summaryBox}
The reporting system can be improved through a centralized database and dashboard-based reporting. The company can begin with dashboards connected to existing Google Sheets and later move important data to a centralized database.
\end{summaryBox}

\subsubsection{Details of Findings}

\begin{itemize}[leftmargin=*]
    \item \textbf{Technical Feasibility:} Google Looker Studio, Microsoft Power BI, Airtable, Zoho Analytics, or a custom dashboard can automate reporting.
    \item \textbf{Economic Feasibility:} Initial cost can be controlled by using existing Google Sheets with dashboard tools.
    \item \textbf{Operational Feasibility:} Managers already use spreadsheets, so dashboard-based reporting will be easier to adopt.
    \item \textbf{Risk Assessment:} Poor data entry discipline can reduce report accuracy.
\end{itemize}

\begin{table}[H]
\centering
\caption{Reporting Improvement -- Estimated Cost-Benefit Analysis}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{5cm}|p{4cm}|X|}
\hline
\rowcolor{secondary}
\textbf{Item} & \textbf{Estimated Annual Cost} & \textbf{Expected Benefit} \\
\hline
Dashboard Tool Setup & BDT 1--2 Lakhs & Faster report generation \\
\hline
Data Cleaning and Standardization & BDT 1 Lakh & Improved data accuracy \\
\hline
Training & BDT 0.5 Lakh & Better user adoption \\
\hline
Manual Reporting Time Reduction & -- & Saves manager and admin time \\
\hline
Error Reduction & -- & Improves decision-making quality \\
\hline
\end{tabularx}
\end{table}

\begin{recommendBox}
\textbf{Priority Action:} Introduce a centralized reporting dashboard.

\textbf{Business Value:} This will improve reporting speed, reduce manual calculation errors, and support faster decision-making.

\textbf{Implementation Note:} Standard data entry rules and validation formats should be introduced before dashboard automation.
\end{recommendBox}

\subsection{Problem 06: Scalability and Dependency Issues}

\begin{problemBox}
The current workflow creates dependency on specific individuals, especially managers who coordinate between clients and developers. If these key individuals are unavailable, work may be delayed.
\end{problemBox}

\begin{summaryBox}
Scalability can be improved by standardizing workflows, documenting processes, and introducing role-based responsibility. This is economically justified because it reduces dependency risk and improves continuity.
\end{summaryBox}

\subsubsection{Details of Findings}

\begin{itemize}[leftmargin=*]
    \item \textbf{Technical Feasibility:} SOPs, onboarding checklists, knowledge bases, and workflow automation can be implemented using Notion, Confluence, Google Drive, or GitHub Wiki.
    \item \textbf{Economic Feasibility:} The main investment is process design, documentation, and training.
    \item \textbf{Operational Feasibility:} The flat structure supports quick decision-making, but growth requires clearer roles and backup responsibility.
    \item \textbf{Risk Assessment:} Documentation may become outdated if not maintained regularly.
\end{itemize}

\begin{table}[H]
\centering
\caption{Scalability Improvement Plan}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{4cm}|X|X|}
\hline
\rowcolor{secondary}
\textbf{Area} & \textbf{Current Issue} & \textbf{Proposed Improvement} \\
\hline
Manager Dependency & Managers handle coordination manually. & Use workflow system and assign backup responsibility. \\
\hline
Employee Onboarding & Knowledge transfer is informal. & Create onboarding checklist and knowledge base. \\
\hline
Process Documentation & Documentation is limited or scattered. & Maintain SOPs in a central repository. \\
\hline
Decision Continuity & Work slows down when key persons are unavailable. & Define role-based approval and escalation process. \\
\hline
\end{tabularx}
\end{table}

\begin{recommendBox}
\textbf{Priority Action:} Create a centralized knowledge base and standard operating procedures.

\textbf{Business Value:} This will support future growth, reduce operational dependency, and make onboarding easier.

\textbf{Implementation Note:} Documentation should be reviewed monthly to keep it updated.
\end{recommendBox}

\section{Comparative Feasibility Summary}

\begin{table}[H]
\centering
\caption{Comparative Feasibility Analysis -- All Six Problems}
\renewcommand{\arraystretch}{1.3}
\small
\begin{tabularx}{\textwidth}{|c|X|c|c|c|c|c|}
\hline
\rowcolor{secondary}
\textbf{No.} & \textbf{Problem} & \textbf{Tech.} & \textbf{Econ.} & \textbf{Ops.} & \textbf{Est. Cost/yr} & \textbf{Priority} \\
\hline
01 & Fragmented System and Lack of Integration & H & H & M & BDT 3--8L & Urgent \\
\hline
02 & Over-Reliance on Informal Communication Channels & H & H & M & BDT 1--3L & High \\
\hline
03 & Unstructured Workflow and Weak Requirement Management & H & H & H & BDT 1--2L & Urgent \\
\hline
04 & Absence of Centralized Task and Project Management System & H & H & H & BDT 2--5L & Urgent \\
\hline
05 & Inefficient Data Management and Reporting & H & M & M & BDT 2--4L & High \\
\hline
06 & Scalability and Dependency Issues & M & H & M & BDT 1--3L & Medium \\
\hline
\end{tabularx}

\vspace{0.2cm}
\small{\textbf{Note:} H = High, M = Medium. Cost values are approximate annual estimates.}
\end{table}

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=0.95\textwidth,
    height=7cm,
    bar width=13pt,
    ymin=0,
    ymax=10,
    ylabel={Feasibility Score},
    symbolic x coords={P01,P02,P03,P04,P05,P06},
    xtick=data,
    nodes near coords,
    nodes near coords align={vertical},
    legend style={at={(0.5,-0.18)}, anchor=north, legend columns=3},
    grid=major,
    major grid style={draw=gray!25},
    title={TEO Feasibility Score by Problem}
]
\addplot[fill=primary!70] coordinates {(P01,9) (P02,8) (P03,10) (P04,10) (P05,7) (P06,7)};
\addplot[fill=accent!70] coordinates {(P01,9) (P02,9) (P03,9) (P04,9) (P05,7) (P06,8)};
\addplot[fill=orange!70] coordinates {(P01,7) (P02,7) (P03,9) (P04,9) (P05,7) (P06,7)};
\legend{Technical, Economic, Operational}
\end{axis}
\end{tikzpicture}
\caption{Technical, Economic, and Operational Feasibility Comparison}
\end{figure}

\section{Recommended Implementation Roadmap}

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tikzpicture}[
    node distance=0.65cm,
    every node/.style={font=\scriptsize},
    phase/.style={
        rectangle,
        rounded corners,
        draw=accent,
        fill=softteal,
        thick,
        text width=2.6cm,
        minimum height=1.1cm,
        align=center
    },
    arrow/.style={thick, -{Latex[length=2.5mm]}, color=primary}
]

\node[phase] (ph1) {Phase 1\\Month 1--2\\Tool Selection};
\node[phase, right=of ph1] (ph2) {Phase 2\\Month 3--4\\Pilot Rollout};
\node[phase, right=of ph2] (ph3) {Phase 3\\Month 5--6\\Integration};
\node[phase, right=of ph3] (ph4) {Phase 4\\Month 7--9\\Documentation};
\node[phase, right=of ph4] (ph5) {Phase 5\\Month 10--12\\Optimization};

\draw[arrow] (ph1) -- (ph2);
\draw[arrow] (ph2) -- (ph3);
\draw[arrow] (ph3) -- (ph4);
\draw[arrow] (ph4) -- (ph5);

\end{tikzpicture}
}
\caption{Proposed Implementation Roadmap}
\end{figure}

\begin{table}[H]
\centering
\caption{Detailed Implementation Roadmap}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|p{3cm}|X|p{3cm}|}
\hline
\rowcolor{secondary}
\textbf{Phase} & \textbf{Major Activities} & \textbf{Duration} \\
\hline
Phase 1 & Select project management platform, create task board, and define requirement template. & Month 1--2 \\
\hline
Phase 2 & Pilot implementation with selected projects and train managers and developers. & Month 3--4 \\
\hline
Phase 3 & Integrate GitHub, communication channels, and reporting dashboards. & Month 5--6 \\
\hline
Phase 4 & Create knowledge base, standard operating procedures, onboarding guide, and backup role structure. & Month 7--9 \\
\hline
Phase 5 & Review performance, collect feedback, and optimize system usage. & Month 10--12 \\
\hline
\end{tabularx}
\end{table}

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    xbar,
    width=0.95\textwidth,
    height=7cm,
    xmin=0,
    xmax=10,
    xlabel={Priority Score},
    symbolic y coords={
        Scalability,
        Reporting,
        Communication,
        Integration,
        Requirement,
        Task Management
    },
    ytick=data,
    nodes near coords,
    grid=major,
    major grid style={draw=gray!25},
    title={Implementation Priority Score}
]
\addplot[fill=accent!75] coordinates {
    (6,Scalability)
    (7,Reporting)
    (8,Communication)
    (9,Integration)
    (10,Requirement)
    (10,{Task Management})
};
\end{axis}
\end{tikzpicture}
\caption{Priority Ranking of Proposed Improvements}
\end{figure}

\section{Conclusion}

The initial feasibility study shows that the major problems identified in NextStepBD's current operational system are solvable through practical and cost-effective information system improvements. The company does not need to replace all existing tools immediately. Instead, it should connect and organize them through a centralized workflow, task management, requirement management, communication, reporting, and documentation structure.

The most urgent improvements are the implementation of a centralized task and project management system, structured requirement management, and integration of disconnected tools. These initiatives directly affect daily productivity, project delivery, accountability, and client satisfaction.

Communication policy and reporting automation should be implemented next, followed by documentation and scalability improvements. Overall, the proposed solutions are technically feasible, economically justified, and operationally realistic. If implemented in phases, the improved system will help NextStepBD achieve stronger coordination, better accountability, faster reporting, improved client satisfaction, and sustainable organizational growth.

\end{document}